---
title: "Comparison of extraction methods"

---

The objective is to compare the extraction capacity of secondary metabolites in two native fruit species: Sambucus australis and Hexachlamys edulis. The methods were: potter homogenizer and another manual with glass rod.

```{r, echo=FALSE,warning = FALSE, message = FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(readxl)
datahv<-read_excel("database.xlsx", sheet="homvar")

datahv$species<-as.factor(datahv$species)
datahv$method<-as.factor(datahv$method)

```

## Descriptive table
```{r  , echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(dplyr)
table_hv<- datahv %>%
  dplyr::group_by(species, method) %>%
  dplyr::summarise(
    mean = mean(phenols),
    min = min(phenols),
    max = max(phenols),
    sd = sd(phenols)
  )


table_hv

```

## Plot
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(ggplot2)
gmc1<-ggplot(data=datahv, aes(x=method, y=phenols, color=species, shape=method))+
  scale_color_manual(values=c("purple4","orange4"))+
  geom_point(size=4)+
  theme_classic()+
  theme(legend.position = "bottom", legend.background = element_rect(fill = "gray12"))+
  theme(panel.grid.major.y = element_line(size=0.05, color='white'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=10, color='white'))+
  theme(axis.text = element_text(color='white'))+
  theme(plot.background = element_rect(fill = "gray12"))+
  theme(panel.background = element_rect(fill = "gray12", color = "white"))+
  ylab("Phenols")+
  xlab("")+
  labs(color = "", shape = "")
gmc1

```

## Model
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

model <- lm(phenols ~ method, data = datahv)

library(lme4)
model_2 <- lmer((phenols) ~ method + (1|species), data = datahv)

library(nlme)

# model_4 <- lme(phenols ~ method, random = ~1|species, weights = varPower(), data = datahv)
# 
# # Crear variable numérica para "method"
# datahv$species_num <- ifelse(datahv$species == "ubajay", 1, 2)
# 
# # Especificar modelo de varianza heterocedástica
# library(nlme)
# model_2 <- lme(phenols ~ method, random = ~1|species, data = datahv, weights = varPower(form = ~ abs(species_num - mean(species_num))))

# AIC(model, model_4, model_5, model_2)

```


## Assumptions
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

hv_ajuste <- as.data.frame(cbind(
  "residuos" = residuals(model_2),
  "predichos" = predict(model_2)))


HVresp<-ggplot(hv_ajuste) +
  aes(predichos, residuos) +
  geom_hline(yintercept = 0, colour="white", size=2) +
  geom_point(colour="white")+
  theme_classic()+
  labs(y="Residuals", x="Predicted values")+
  theme(legend.position = "bottom", legend.background = element_rect(fill = "gray12"))+
  theme(panel.grid.major.y = element_line(size=0.05, color='white'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=10, color='white'))+
  theme(axis.text = element_text(color='white'))+
  theme(plot.background = element_rect(fill = "gray12"))+
  theme(panel.background = element_rect(fill = "gray12", color = "white"))
HVresp

QQresp<-ggplot(hv_ajuste) +
  aes(sample = residuos) +
  geom_qq(shape = 1, colour="white") +
  geom_qq_line(colour="white")+
  theme_classic()+
  labs(y="Sample Quantiles", x="Theoretical Quantiles")+
  theme(legend.position = "bottom", legend.background = element_rect(fill = "gray12"))+
  theme(panel.grid.major.y = element_line(size=0.05, color='white'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=10, color='white'))+
  theme(axis.text = element_text(color='white'))+
  theme(plot.background = element_rect(fill = "gray12"))+
  theme(panel.background = element_rect(fill = "gray12", color = "white"))
QQresp

e<-resid(model_2) # residuos de pearson
pre<-predict(model_2) #predichos
shapiro.test(e)
library(car)
leveneTest(phenols~method*species, datahv)

```

## Mean comparison
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
anova(model_2)
```

# Carotenoids
The objective is to compare the extraction capacity of carotenoids. The methods were: potter homogenizer with 5ml solution (potter_A), potter homogenizer with 9ml solution (potter_B) and another manual with glass rod.

```{r, echo=FALSE,warning = FALSE, message = FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(readxl)
datahvcar<-read_excel("database.xlsx", sheet="homvarcar")
datahvcar$method<-as.factor(datahvcar$method)

```

## Descriptive table
```{r  , echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(Rmisc)
table_hvcar <- summarySE(datahvcar, measurevar="caroten", groupvars=c("method"))
table_hvcar

```

## Plot
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(ggplot2)
gmc1car<-ggplot(data=datahvcar, aes(x=method, y=caroten, color=method, shape=method))+
  scale_color_manual(values=c("red","orange","blue"))+
  geom_point(size=4)+
  theme_classic()+
  theme(legend.position = "bottom", legend.background = element_rect(fill = "gray12"))+
  theme(panel.grid.major.y = element_line(size=0.05, color='white'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=10, color='white'))+
  theme(axis.text = element_text(color='white'))+
  theme(plot.background = element_rect(fill = "gray12"))+
  theme(panel.background = element_rect(fill = "gray12", color = "white"))+
  ylab("Carotenoids fresh weight")+
  xlab("")+
  labs(color = "", shape = "")
gmc1car

```

## 
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

model_caroten <- lm(caroten ~ method, data=datahvcar)

```

## Mean comparison
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
anova(model_caroten)
```

## Tukey
```{r  , echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(emmeans)
# library(multcompView)
Comptar<-emmeans(model_caroten, pairwise ~ method) #Tukey  
Comptar
plot(Comptar, comparisons = TRUE)+
  labs(x = "Carotenoids [µg / g fruit fresh weight]", y ="Method")+
  theme_classic()+
  ggtitle("Mean Contrast")+
  theme(plot.title = element_text(hjust = 0.5, size = rel(1), color = "black"))+
  scale_fill_manual(values = c("red","orange","blue")) +
  theme(legend.position='none')+
  theme(panel.grid.major.y = element_line(color="grey", size=4))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=14, color='black'))+
  theme(axis.text = element_text(color='black', size=14))+
  annotate("text", x = table_hvcar$caroten[table_hvcar$method == "potter_A"]
, y = 1.3 , label = "a")+
  annotate("text", x = table_hvcar$caroten[table_hvcar$method == "potter_B"]
, y = 2.3, label = "a")+
  annotate("text", x = table_hvcar$caroten[table_hvcar$method == "rod"]
, y = 3.3, label = "b")

```

