---
title: "Polinización"
---

## Objetive
The objective of this essay was to study the pollination regime of the species.

## Materials and Methods
Pollination studies were carried out on floral buds that had not begun anthesis yet. In the **natural self-pollinated** (NSPO) treatment, branches with only one bud were isolated with paper bags , in **natural self-pollinated** (NSPS) branches with several buds were isolated with paper bags to check auto compatibility, while in the **open pollination** (OP) treatment branches were only identified. In the **cross-pollinated** (CPA) trial, buds were emasculated and then pollinated manually with pollen from another genotype and in **cross pollinated** (CPS) the buds were emasculated and then pollinated manually with pollen from anothers flowers on the same genotype. These branches were also covered with paper bags to avoid the entrance of unknown pollen. Twenty repetitions of each treatment were performed in random branches. Finally, thirty days later fruit set was verified.
 
## Results
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
library(readxl)
data<-read_excel("database.xlsx", sheet = "III poliniza")

data$Tratamiento <- factor(data$Tratamiento,
                   levels = c("Libre", "Auto","Auto *", "Cruzado =","Cruzado *"),
                   labels = c("[OP]", "[NSPO]","[NSPS]", "[CPS]","[CPA]"))

# "[O]", "[NSB]","[NSG]", "[ASG]","[AC]"

data$Tratamiento<-as.factor(data$Tratamiento)
data$Ef<-as.numeric(data$Ef)
data$Tratamiento<-factor(data$Tratamiento,levels=c("[NSPO]","[NSPS]","[OP]","[CPA]", "[CPS]"))

### Pollination efficiency per treatment
library(ggplot2)
# color=c("coral4","coral","chocolate","chocolate4","tan3","chocolate1")
# G<-ggplot(data=data, aes(x=Tratamiento, y=Ef, fill=Tratamiento)) +
#   geom_bar(stat="identity", position="stack", width=0.1) +
#   theme_classic()+
#   labs(y="Efficiency (%)", x="Treatment")+
#   scale_fill_manual(values = c("coral4","coral","chocolate","chocolate4","tan3"))+
#   theme(text = element_text(size=20))+
#   theme(legend.title=element_blank())+
#   theme(legend.position = "none")+
#   theme(panel.grid.major.y = element_line(size=0.05, color='black'))+
#   theme(panel.grid.major.x = element_blank())+
#   theme(text = element_text(size=20, color='black'))+
#   theme(axis.text = element_text(color='black'))+
#   ylim(0,25)
# G
```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# datapol<-read.delim("datapol.txt")

```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

datapol<-read_excel("database.xlsx", sheet = "III polin")

datapol$TRA <- factor(datapol$TRA,
                   levels = c("NSPO","NSPS","OP","CPA", "CPS"))

library(ggplot2)
# color=c("coral4","coral","chocolate","chocolate4","tan3","chocolate1")
G2<-ggplot(data=datapol, aes(x=TRA, y=PROP, fill=TRA)) +
  geom_bar(stat="identity", position="stack", width=0.1) +
  theme_classic()+
  labs(y="Fruit set ratio", x="Treatment")+
  scale_fill_manual(values = c("coral4","coral","chocolate","chocolate4","tan3"))+
  theme(text = element_text(size=20))+
  theme(legend.title=element_blank())+
  theme(legend.position = "none")+
  theme(panel.grid.major.y = element_line(size=0.05, color='black'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=20, color='black'))+
  theme(axis.text = element_text(color='black'))
G2

# library(ggplot2)
# p <- ggplot(datapol, aes(TRA, PROP, colour = TRA ))
# p +  geom_point() + labs(x = "") + labs(y = "CUAJE")+
#   theme_classic()

```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# datapol2<-subset(datapol, TRA == "OP")
# datapol3<-subset(datapol, TRA == "CPA")
# datapol4<-rbind(datapol2, datapol3)
# 
# mpol2b <- glm(PROP ~ TRA,
#           family = "binomial",
#           data = datapol4)
# 
# summary(mpol2b)
# 
# library(sjPlot)
# plot_model(mpol2b, show.values = TRUE)+
#   theme_classic()+
#   theme(text = element_text(size=20))+
#   theme(legend.title=element_blank())+
#   theme(legend.position = "none")+
#   theme(panel.grid.major.y = element_line(size=0.05, color='black'))+
#   theme(panel.grid.major.x = element_blank())+
#   theme(text = element_text(size=20, color='black'))+
#   theme(axis.text = element_text(color='black'))


```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(readxl)
polin<-read_excel("database.xlsx", sheet = "III polin")

polin$Tratamiento <- as.factor(polin$TRA)

```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(glmmTMB)  # Para modelos cero-inflados

# Ajustar un modelo de regresión logística cero-inflado
# model <- glmmTMB(PROP ~ Tratamiento, data = polin, weights = TOTAL,  family = binomial())
model <- glm(PROP ~ Tratamiento, data = polin, weights = TOTAL,  family = "quasibinomial")

#Supuestos
RP <- resid(model, type = "pearson") #"Residuos de pearson
ajust<-fitted(model) #predichos en escala de Y

#Grafico de residuos vs predichos
plot(ajust, RP,xlab="predichos", ylab= "Residuos de pearson", main="Gráfico de RP vs PRED", cex.main=.8)
#Distancia de Cook
plot(model, which = c(4)) 

#Sobre o subdispersion?
sum(RP^2) / (model$df.res)

# Si bien hay subdispersión (aumento de la probabilidad de error tipo II) es más dificil de encontrar diferencias, todo se vuelve menos significativo y a pesar de esto se encuentran las diferencias. Es evidente que en los 3 tratamientos en los que no se evidenció ningun fruto no habrá significancia más alla de sobre o sub dispersión de los datos.

```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

summary(model)

# Anova del modelo
library(car)

Anova(model)

drop1(model, test = "Chi")
drop1(model, test = "LRT")

library(emmeans)
emmeans(model, pairwise ~ Tratamiento, type ="response")

```
Plot 1

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# Grafico del modelo ajustado
library(ggplot2)
gg_polin <- ggplot(polin, aes(Tratamiento, PROP,colour = Tratamiento )) +
  geom_point()+ geom_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE) + labs(x = "Tratamiento de polinización") + labs(y = "Cuajado") 
gg_polin

```

Plot 2

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=15, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# 
library(sjPlot)
plot_polin <- plot_model(model, show.values = TRUE)+
  theme_classic()+
  theme(text = element_text(size=20))+
  theme(legend.title=element_blank())+
  theme(legend.position = "none")+
  theme(panel.grid.major.y = element_line(size=0.05, color='black'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=20, color='black'))+
  theme(axis.text = element_text(color='black'))
plot_polin

```

## Conclusion

Only treatments **open pollination [OP]** (5.56%) and **artificial cross-pollinated [CPA]** (21.28%) presented fruit set. Therefore the species is self-incompatible.