---
title: "Yield"
---

The fruit harvest was staggered in three weeks corresponding to the second, third and fourth week of December of the years 2019, 2020 and 2021. The fruits of each individual were weighed to compare yields between years by ANOVA.

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=30, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
library(readxl)
data<-read_excel("database.xlsx", sheet="III rendmor")

data$YEAR<-as.factor(data$YEAR)
data$ACC<-as.factor(data$ACC)
data$WEEK<-as.factor(data$WEEK)
data$WEEK<-factor(data$WEEK,levels=c("1","2","3"))
data$DATE<-as.Date(data$DATE, format="%m/%d/%y")
data$N<-as.numeric(data$N)

```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=30, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

dataY2<-read_excel("database.xlsx", sheet="III rendmor2")
dataY2$YEAR<-as.factor(dataY2$YEAR)
dataY2$ACC<-as.factor(dataY2$ACC)
dataY2$P<-as.numeric(dataY2$P)


```

# Average fresh weight (g) per plant.

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(ggplot2)
Y0<- ggplot(dataY2, aes(x=ACC, y=P, fill=YEAR)) +
  stat_summary(fun = "mean", size = 1, geom = "bar", position="dodge", width=0.5) +
  scale_fill_manual(values=c("coral", "grey","green4"))+
  # geom_errorbar(aes(ymin=P-sd, ymax=P+sd), width=0.2, position=position_dodge(.5))+
  labs(y="Fresh weight (g)", x="Genotype")+
  theme_classic()+
  theme(legend.position = "bottom")+
  theme(panel.grid.major.y = element_line(size=0.05, color='black'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=20, color='black'))+
  theme(axis.text = element_text(color='black'))+
  ylim(0,2200)
  # geom_text(aes(label = round(P,0)), vjust = 1.5, hjust = -0.2, size=7)
Y0

```

# Bars plot.
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=11}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

datas2<-  data #subset(data, YEAR == 2019 | YEAR == 2020)

levels(datas2$WEEK) <- c("8 al 14 de diciembre", "15 al 21 de diciembre", "22 al 28 de diciembre")

# library(tidyverse)
library(ggplot2)
gg_yield_week <- gg_yield_week <- ggplot(data = datas2, aes(x = WEEK, y = P, fill = ACC)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = ifelse(is.na(N), "", N)), 
            position = position_dodge(width = 0.9), 
            vjust = -0.5, 
            size = 5, 
            color = "black") +
  scale_y_continuous(limits = c(0, 1300), 
                    breaks = seq(0, 1250, by = 250), 
                    name = "Peso fresco (g)") +
  labs(
    x = "", 
    fill = "Número de planta"
  ) +
  theme_classic() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(size = 0.05, color = "black"),
    text = element_text(size = 30, color = "black"),
    axis.text = element_text(color = "black"),
    legend.position = "bottom", 
    legend.text = element_text(size = 15)
  ) +
  facet_grid(YEAR ~ .) +
  scale_fill_viridis_d(option = "D", end = 0.8)

gg_yield_week

# ggsave("gg_yield_week", plot = gg_yield_week, device = "tiff", width = 16, height = 8, units = "in", dpi = 300)

```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=30, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)



```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=11}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

f1s<-ggplot(data=datas2, aes(x=YEAR, y=P, fill=ACC)) + 
  geom_bar(stat="identity", position="dodge")+
  # scale_fill_manual(values=c("coral", "grey","green4"))+
  # geom_point(size=3, shape=20) +
  labs(y="Fresh Weigth (g)", x="Year")+
  theme(panel.grid.major.x = element_blank())+
  facet_grid(WEEK~.)+
  theme_classic()+
  theme(text = element_text(size=20))+
  theme(legend.title=element_blank())+
  theme(legend.position = "bottom")+
  theme(panel.grid.major.y = element_line(size=0.05, color='black'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=30, color='black'))+
  theme(axis.text = element_text(color='black'))
f1s

```

# Bars plot.
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=11}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# library(tidyverse)
library(ggplot2)
f1B<-ggplot(data=dataY2, aes(x=YEAR, y=P, fill=ACC)) + 
  geom_bar(stat="identity", position="dodge")+
  labs(y="WEIGHT (g)", x="YEAR")+
  theme(panel.grid.major.x = element_blank())+
  theme_classic()+
  theme(text = element_text(size=20))+
  theme(legend.title=element_blank())+
  theme(legend.position = "bottom")+
  theme(panel.grid.major.y = element_line(size=0.05, color='black'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=20, color='black'))+
  theme(axis.text = element_text(color='black'))
f1B

```

# Decriptive table for years
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(Rmisc)
dataY<-subset(data, P >= 00.001)
estadY <- summarySE(dataY2, measurevar="P", groupvars=c("YEAR"))
estadY


```

# Average plant fresh weight (g) per year.

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=10, fig.height=8}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

P3<- ggplot(estadY, aes(x=YEAR, y=P, fill=YEAR)) +
  stat_summary(fun = "mean", size = 0.5, geom = "bar") +
  scale_fill_manual(values=c("coral", "grey","green4"))+
  geom_errorbar(aes(ymin=P-sd, ymax=P+sd), width=0.2, position=position_dodge(.5))+
  labs(y="Average fresh weight (g) per plant", x="Year")+
  theme_classic()+
  theme(legend.position = "none")+
  theme(panel.grid.major.y = element_line(size=0.05, color='black'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=20, color='black'))+
  theme(axis.text = element_text(color='black'))+
  ylim(0,1500)+
  geom_text(aes(label = round(P,0)), vjust = 1.5, hjust = -0.2, size=7)
P3

```
The bars indicate standard deviation.


```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)
# Boxplots of Weights (g) of harvested fruits, with comparison of seasons in each accession.
# f2<-ggplot(data=data, aes(x=ACC, y=P, fill=YEAR)) +
#   geom_boxplot(size=.5)+
#   scale_fill_manual(values=c("coral", "grey","green4"))+
#   labs(y="PESO (g)", x="ACCESIÓN")+
#   theme(panel.grid.major.x = element_blank())+
#   theme_classic()+
#   theme(text = element_text(size=20))+
#   theme(legend.title=element_blank())+
#   theme(legend.position = "bottom" )+
#   geom_hline(aes(yintercept=0), color="darkgrey")+
#   geom_hline(aes(yintercept=300), color="grey")+
#   geom_hline(aes(yintercept=600), color="grey")+
#   geom_hline(aes(yintercept=900), color="grey")+
#   geom_hline(aes(yintercept=1200), color="darkgrey")
# f2

```


```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# Average total yield of each accession per season.
# f3<-ggplot(data=data, aes(x=ACC, y=P, color=ACC)) +
#   geom_boxplot(size=.5)+
#   labs(y="PESO (g)", x="ACCESIÓN")+
#   theme(panel.grid.major.x = element_blank())+
#   theme_classic()+
#   theme(text = element_text(size=20))+
#   theme(legend.title=element_blank())+
#   theme(legend.position = "none")+
#   geom_hline(aes(yintercept=0), color="darkgrey")+
#   geom_hline(aes(yintercept=300), color="grey")+
#   geom_hline(aes(yintercept=600), color="grey")+
#   geom_hline(aes(yintercept=900), color="grey")+
#   geom_hline(aes(yintercept=1200), color="darkgrey")
# f3

```


```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# Average yield of the mount in each season.
# f4<-ggplot(data=data, aes(x=YEAR, y=P, fill=YEAR)) +
#   geom_boxplot(size=.3)+
#   geom_point(size=3, shape=20) +
#   # scale_color_manual(values=c("coral", "grey","green4"))+
#   scale_fill_manual(values=c("coral", "grey","green4"))+
#   labs(y="PESO POR PLANTA PROMEDIO", x="AÑO DE COSECHA")+
#   theme_classic()+
#   theme(text = element_text(size=20))+
#   theme(legend.title=element_blank())+
#   theme(legend.position = "bottom" )
# f4

```

# Inferential Statistics

## Model and assumptions
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)


mY2<-lm(data=dataY2, sqrt(P)~YEAR)
mY2

Y_ajuste <- as.data.frame(cbind(
  "residuos" = residuals(mY2),
  "predichos" = predict(mY2)))

Y_ajuste$P <- dataY2$P

library(ggplot2)
HVY<-ggplot(Y_ajuste) +
  aes(predichos, residuos) +
  geom_hline(yintercept = 0, colour="white", size=2) +
  geom_point(colour="white", size=2)+
  theme_classic()+
  labs(y="Residuals", x="Predicted values")+
  theme(legend.position = "bottom", legend.background = element_rect(fill = "gray12"))+
  theme(panel.grid.major.y = element_line(size=0.05, color='white'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=10, color='white'))+
  theme(axis.text = element_text(color='white'))+
  theme(plot.background = element_rect(fill = "gray12"))+
  theme(panel.background = element_rect(fill = "gray12", color = "white"))
HVY

QQY<-ggplot(Y_ajuste) +
  aes(sample = residuos) +
  geom_qq(shape = 1, colour="white", size=2) +
  geom_qq_line(colour="white")+
  theme_classic()+
  labs(y="Sample Quantiles", x="Theoretical Quantiles")+
  theme(legend.position = "bottom", legend.background = element_rect(fill = "gray12"))+
  theme(panel.grid.major.y = element_line(size=0.05, color='white'))+
  theme(panel.grid.major.x = element_blank())+
  theme(text = element_text(size=10, color='white'))+
  theme(axis.text = element_text(color='white'))+
  theme(plot.background = element_rect(fill = "gray12"))+
  theme(panel.background = element_rect(fill = "gray12", color = "white"))
QQY

e<-resid(mY2) # residuos de pearson
pre<-predict(mY2) #predichos
shapiro.test(e)

```

## ANOVA
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

anova(mY2)

```

There is no significant difference between years

# Modelo de rendimiento en función del volummen de copa
```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)


library(dplyr)

# Sumar N y P por ACC y YEAR
result <- data %>%
  dplyr::group_by(YEAR, ACC) %>%
  dplyr::summarise(
    total_N = sum(N, na.rm = TRUE),
    total_P = sum(P, na.rm = TRUE),
    .groups = "drop"
  )

# Mostrar el resultado
print(result)

```


```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

data_car <- data.frame(
  ACC = 1:15,
  Altura = c(4.02, 3.1, 3.2, 4, 4.7, 3.70, 1.9, 2.9, 4.4, 4.25, 4.4, 6, 3.1, 3.4, 3.3),
  DAP = c(22, 11.8, 13, 17, 18, 11.5, 1, 6.5, 22.8, 17.5, 12.5, 25, 8.5, 8, 11),
  DM = c(4, 2.6, 2.9, 2.5, 3, 3.2, 1.2, 2.3, 2.6, 3.5, 3, 2.7, 2.1, 2.5, 2.3),
  Dm = c(2, 2.3, 2.1, 1.8, 1.7, 2.1, 1.1, 2.2, 2.7, 2.9, 2.4, 1.9, 1.6, 1.8, 1.6)
)

data_car$ACC <- as.factor(data_car$ACC)
# data_car$Altura <- data_car$Altura*100
# data_car$DM <- data_car$DM*100
# data_car$Dm <- data_car$Dm*100
data_car$Vol <- (2/3) * 3.14159 * data_car$Altura * ((data_car$DM/2) * (data_car$Dm/2))
# data_car$DAP <- data_car$DAP/3.14159

```


```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

library(dplyr)

# Sumar P por planta (ACC) y año (YEAR)
p_sum_by_acc_year2 <- data %>%
  dplyr::group_by(ACC, YEAR) %>%
  dplyr::summarise(
    P_total = sum(P, na.rm = TRUE),
    .groups  = "drop"
  )

p_sum_by_acc_year <- p_sum_by_acc_year2 %>%
  dplyr::group_by(ACC) %>%
  dplyr::summarise(
    P_medio = mean(P_total, na.rm = TRUE),
    .groups  = "drop"
  )


# 1. Hacer el merge entre la suma de P por planta/año y las covariables
datos_reg <- p_sum_by_acc_year %>%
  dplyr::inner_join(data_car,
                    by = c("ACC"))
```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

numeric_vars <- datos_reg[, c("P_medio","Altura", "DAP", "DM", "Dm", "Vol")]

# Calcular la matriz de correlación
correlation_matrix <- cor(numeric_vars, method = "pearson", use = "complete.obs")

# Mostrar la matriz de correlación
print(correlation_matrix)

# Opcional: Visualizar la matriz de correlación con corrplot
# Instalar el paquete corrplot si no está instalado: install.packages("corrplot")
library(corrplot)
corrplot(correlation_matrix, method = "circle", type = "upper", 
         addCoef.col = "black", tl.col = "black", tl.srt = 45)


```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

# 1) Define el modelo global con todas las interacciones de pares:
modelo_global_int <- lm(
  P_medio ~ (Altura + DAP + DM + Dm + Vol)^2,
  data = datos_reg
)

library(MuMIn)
options(na.action = "na.fail")

dredge_int2 <- dredge(
  modelo_global_int,
  m.lim = c(1, 8),
  trace = FALSE
)

head(dredge_int2, 10)

# 5) Extrae el modelo Top‐1 con interacción:
best_int <- get.models(dredge_int2, 1)[[1]]
summary(best_int)


```

```{r, echo=FALSE, fig.align='center', fig.asp=0.4, fig.width=20, fig.height=12}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

data4 <- datos_reg[,c(1,7)]

library(dplyr)

# Opción 1: partir de p_sum_by_acc_year2 y añadir Vol desde data4
merged_df <- result %>%
  dplyr::inner_join(data4, by = "ACC")

merged_df$P_Vol <- merged_df$total_P/(merged_df$Vol)

merged_df$P_Vol <- round(merged_df$P_Vol,0)

# library(tidyverse)
#Gráfico de rendimiento peso y número de frutos por árbol año
library(ggplot2)
gg_yield_year <- ggplot(data = merged_df, aes(x = YEAR, y = total_P , fill = ACC)) + 
  geom_bar(stat = "identity", position = "dodge") +
  geom_hline(yintercept = 743.0222, color = "#B2DF8A", linetype = "dashed", size = 1.5) +
  geom_text(aes(label = ifelse(is.na(total_N), "", total_N )), 
            position = position_dodge(width = 0.9), 
            vjust = 1, 
            size = 7, 
            color = "red") +
  geom_text(aes(label = ifelse(is.na(P_Vol), "", P_Vol )), 
            position = position_dodge(width = 0.9), 
            vjust = -0.8, 
            size = 7, 
            color = "black") +
  scale_y_continuous(limits = c(0, 2250), 
                    breaks = seq(0, 2250, by = 250), 
                    name = "Peso fresco (g)") +
  labs(
    x = "", 
    fill = "Número de planta"
  ) +
  theme_classic() +
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_line(size = 0.05, color = "black"),
    text = element_text(size = 30, color = "black"),
    axis.text = element_text(color = "black"),
    legend.position = "bottom", 
    legend.text = element_text(size = 15)
  ) +
  # facet_grid(. ~ YEAR) +
  scale_fill_viridis_d(option = "D", end = 0.8)

  # geom_hline(yintercept = 74.88889, color = "black", linetype = "dashed", size = 1.5) +
  # geom_hline(yintercept = 36.44444, color = "red", linetype = "dashed", size = 1.5) +

gg_yield_year


```

